DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-03-01 rebuttal.tex

\subsection{}
\begin{mdframed}[style=comment]
As such, the SHT is only performed once on the input (no back and forth SHT between each layer). While this clever trick lowers the complexity of the convolution to $\mathcal{O}(N_{pix})$, the non-linearity is $\mathcal{O}(N^{3/2}_{pix})$.

- I don't understand what the difference is between the convolution and the "non-linearity". I think this sentence either needs explaining further. Is the process $\mathcal{O}(N_{pix})$ or $\mathcal{O}(N^{3/2}_{pix})$?
\end{mdframed}

In \cite{kondor2018clebsch}, the convolution is performed in the spectral (harmonic) domain with a simple Hadamard product.
Instead of recomposing the signal and applying a traditional non-linearity such as the ReLU in the pixel domain, \cite{kondor2018clebsch} proposes to apply a Clebsch–Gordan product in the spectral domain.
(As a non-linear operation preserving rotation equivariance, it is considered as the non-linearity of the NN.)
Their convolution costs $\mathcal{O}(N_{pix})$, and their non-linearity costs $\mathcal{O}(N^{3/2}_{pix})$.
Stacking those layers result in a NN of overall $\mathcal{O}(N^{3/2}_{pix})$ time complexity.
We clarified the sentence.

\subsection{}
\begin{mdframed}[style=comment]
When mentioning that you are 10 to 20 times faster than the SHT it should be noted that libsharp has amazing distributed mpi functionality which helps, although of course your method is genuinely lower order computationally (and can be distributed simply on a GPU).
\end{mdframed}

True.
In the experiment, both were compared on a single core.
They might however scale differently given one can be distributed through MPI and the other on a GPU.
The manuscript was updated.

### 2019-03-01 scnn.tex
comment 2.10

Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the vector $\f$ with the sparse matrix $\tL$.
The cost of one such multiplication is $\bO(|\E| + |\V|)$.
By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution reduces to $\bO(N_{pix})$ operations and as such is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform.
This is especially true for smooth kernels which require a low polynomial degree $K$.
\figref{filtering_speed} compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
A naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform at $\ell_{max} = 3 N_{side}$ implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.

>>>>

Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the vector $\f$ with the sparse matrix $\tL$.
The cost of one such multiplication is $\bO(|\E| + |\V|)$.
By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution reduces to $\bO(N_{pix})$ operations and as such is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform.
This is especially true for smooth kernels which require a low polynomial degree $K$.
\figref{filtering_speed} compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
On a single core, a naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform at $\ell_{max} = 3 N_{side}$ implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.
Note that the two might however scale differently, given that \pkg{libsharp} can be distributed on CPUs through MPI while our method can be distributed on GPUs by \pkg{TensorFlow}.
